\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{bm}

\geometry{margin=1in}

\title{Formalizing Sovereign Informatic Manifolds: \\ Anisotropically Frustrated Gradient Flows and Timing Protocols}
\author{Sovereign Stack Architect}
\date{April 2026}

\begin{document}

\maketitle

\begin{abstract}
We present a formal framework for the Sovereign Informatic Manifold, an architectural substrate for verified recursive evolution. We derive the governing equations for anisotropically frustrated torsional gradient flows and map these dynamics to hardware-level memory timing protocols (FAMM). By anchoring informatic state in formal differential geometry, we achieve system-wide forensic auditability and stability boundaries.
\end{abstract}

\section{The Informatic Manifold}
Let $\mathcal{M}$ be an $n$-dimensional manifold representing the informatic state space. We define a metric $g_{ij}$ and a torsion tensor $T^k_{ij}$ that characterize the local connectivity and "snagging" of information during transport.

\subsection{Governing Equations}
The evolution of the hyperfluid phase field $\phi(x,t)$ and the embedding $X^A(x,t)$ are governed by:
\begin{equation}
    \partial_t \phi = \nabla_i(M^{ij} \nabla_j \frac{\delta F}{\delta \phi}) - \sigma \frac{\partial \phi}{\partial I_{lock}}
\end{equation}
\begin{equation}
    \partial_t X^A = -\Gamma^A_{BC} \partial_i X^B \partial_i X^C - \Lambda^{AB}(X^B - X_0^B) - \frac{\delta F}{\delta X^A} + \tau T^A
\end{equation}
where $I_{lock}$ is the interlocking energy potential and $X_0$ is the preferred "fold-back" location in the ambient $n$-space.

\section{Anisotropy and Frustrated Relaxation}
We introduce the anisotropy tensor $A^{ij}$ to model the frustration that prevents the manifold from reaching a trivial global minimum. This frustration creates metastable local minima which serve as persistent informatic "snags."

\subsection{Interlocking Energy}
The energy of a state is frustrated by the previous configuration, leading to the interlocking potential:
\begin{equation}
    I_{lock}(X) = W(X - X_{prev}; A)
\end{equation}
where $W$ is a periodic weight function modulated by $A$.

\section{Frustration-Aware Manifold Memory (FAMM)}
We translate these manifold invariants into hardware-level timing parameters.

\subsection{Dynamic Timing Derivations}
The timing parameters for the memory controller are derived as follows:
\begin{itemize}
    \item \textbf{Phantom Tide Timing Correction ($t_{PT}$)}: 
    \begin{equation}
        t_{PT} = t_{Base} \cdot (1 - \lambda \cdot v)
    \end{equation}
    where $v$ is the nodal velocity and $\lambda = 0.7$ is the Phantom Tide dampening constant. This ensures hardware-level stability under high-velocity informatic noise (Dolphin Principle).
\end{itemize}

where $\text{Score}_{\Sigma+NK}$ incorporates both the torsional stress $\Sigma$ and the non-isotropic (NK) informatic coupling.

\subsection{Formal Stability and ACI Preservation}
We prove that the MLGRU transition preserves the Anti-Collision Identity (ACI) stability. For a hidden state $h \in \mathcal{M}^N$ satisfying $\text{ACI}(h) \le \epsilon$, and a candidate state $c$ likewise satisfying $\text{ACI}(c) \le \epsilon$, the update rule $h' = f \odot h + (1-f) \odot c$ ensures:
\begin{equation}
    |h'_i - h'_j| \le f|h_i - h_j| + (1-f)|c_i - c_j| \le \epsilon
\end{equation}
provided the forget gate $f$ is spatially uniform. This result guarantees the structural integrity of the manifold against "folding collisions" during rapid expansion.

\subsection{The Unified Manifold-Blit Equation}
To enable hardware-native shortcuts across the manifold, we utilize the Unified Manifold-Blit Equation:
\begin{equation}
    \mathcal{B}(X_{t+1}) = \text{Blit}(\mathcal{F}(X_t), A, T)
\end{equation}
where $\mathcal{B}$ represents the hardware-mapped frustration energy at ports $M[-23..-25]$.

\section{Conclusion}
The formal bridge between discrete braid accumulation and geometric torsion allows for a formally verified, hardware-native execution engine. The Sovereign Informatic Manifold ensures that every state transition is a lawful move in the underlying semantic space, preventing stochastic drift and ensuring total forensic auditability.

\end{document}
